\documentclass[../main]{subfiles}
%\usepackage{url}
\setcounter{section}{1}
\begin{document}
\begin{thebibliography}{99}
\bibitem{shimada_paper1} 島田滉己，上田隆一，林原靖男，”トポロジカルマップを用いたシナリオによるナビゲーションの提案 ー人が道案内に用いる情報の取得と評価ー”，日本機械学会ロボティクス・メカトロニクス講演会'20予稿集，2P1-K02（2020）
\bibitem{shimada_paper2} 島田滉己，上田隆一，林原靖男，”トポロジカルマップを用いたシナリオによるナビゲーションの提案 ーシナリオに基づく実ロボットのナビゲーションー”，1H2-04，SI2020（2020）
\bibitem{toe_finding_algolithm} Chen,Tongtong,etal.“Lidar-based long range road intersection detection. ”2011 Sixth International Conferenceon Imageand Graphics.IEEE,(2011)
\bibitem{yolo_paper_v1} Redmon, Joseph, et al. "You only look once: Unified, real-time object detection." Proceedings of the IEEE conference on computer vision and pattern recognition. 2016.
\bibitem{yolo_paper_v2} Redmon, Joseph, and Ali Farhadi. "YOLO9000: better, faster, stronger." Proceedings of the IEEE conference on computer vision and pattern recognition. 2017.
\bibitem{yolo_paper_v3} Redmon, Joseph, and Ali Farhadi. "Yolov3: An incremental improvement." arXiv preprint arXiv:1804.02767 (2018).
\bibitem{yolo_paper_v4} Bochkovskiy, Alexey, Chien-Yao Wang, and Hong-Yuan Mark Liao. "Yolov4: Optimal speed and accuracy of object detection." arXiv preprint arXiv:2004.10934 (2020).
\bibitem{kanrenkenkyuu1} 澤橋遼太，細田佑樹，町中希彰，山崎亮太，定國裕大，草刈亮輔，黒田洋司(2018)Edge-Node-Graph 及び分岐点検出に基づく道なり走行ナビゲーションシステムの開発 第 23 回ロボティクスシンポジア No.18-3，pp.67-72
\bibitem{yolov5} YOLOv5: https://github.com/ultralytics/yolov5
\bibitem{yolov5_figure} Luo, Y., Zhang, Y., Sun, X., Dai, H., \& Chen, X. (2021). Intelligent Solutions in Chest Abnormality Detection Based on YOLOv5 and ResNet50. Journal of healthcare engineering, 2021, 2267635. \url{https://doi.org/10.1155/2021/2267635}
\bibitem{kokudotiriin} 国土地理院: 基盤地図情報ダウンロードサービス, \url{https://maps.gsi.go.jp/development/ichiran.html}
\bibitem{cnn_paper} LeCun，Yann，et al．"Gradient-based learning applied to document recognition．" Proceedings of the IEEE 86．11 (1998): 2278-2324．
\end{thebibliography}
\end{document}